---
title: "lmcpp_test - Homework 4 Test"
output: html_document
---

This is an [RMarkdown](https://rmarkdown.rstudio.com/) notebook created with [RStudio](https://rstudio.com) to test Homework 4 of BIOSTAT625.

---

## Preambles

### Install the package and the benchmarking package for efficiency check
```{r}
install.packages('lmrewrt.tar.gz',repos=NULL)
install.packages("microbenchmark")
```

### Load the package.
```{r}
library(lmrewrt)
library("microbenchmark")
```

### Check the help files
```{r}
help(lm.rewrt)
help(summary.lm.rewrt)
```

### load test input data1
```{r}
data(cars)
```

### create a simple linear model and summarize the regression output
```{r}
fit1 = lm.rewrt(dist ~ speed, data = cars, prt = TRUE)
summ1 = summary.lm.rewrt(fit1, correlation = TRUE, prt = TRUE)
```

### load test input data2
```{r}
data(mtcars)
```

### create a multiple linear model and summarize the regression output
```{r}
fit2 = lm.rewrt(mpg ~ cyl + hp, data = mtcars, prt = TRUE)
summ2 = summary.lm.rewrt(fit2, correlation = TRUE, prt = TRUE)
```

### test of correctness of lmcpp/summary.lmcpp comparing to the original function (lm/summary.lm)
```{r}
fit.lm1 = lm(dist ~ speed, data = cars)
fit.lm2 = lm(mpg ~ cyl + hp, data = mtcars)
fit.summ1 = summary(fit.lm1, correlation = TRUE)
fit.summ2 = summary(fit.lm2, correlation = TRUE) 
for ( i in c("coefficients","df.residual","fitted.values","residuals") ) {
  print( all.equal(fit1[[i]], fit.lm1[[i]]) )
  print( all.equal(fit2[[i]], fit.lm2[[i]]) )
}
for ( j in c("adj.r.squared", "coefficients", "correlation", "cov.unscaled", "fstatistic", "r.squared", "residuals", "sigma") ) {
  print( all.equal(summ1[[j]],fit.summ1[[j]]))
  print( all.equal(summ2[[j]],fit.summ2[[j]]))
}
```

### test of efficiency of lmcpp/summary.lmcpp comparing to the original function (lm/summary.lm)
```{r}
microbenchmark(lm.rewrt(dist ~ speed, data = cars),lm(dist ~ speed, data = cars))
microbenchmark(lm.rewrt(mpg ~ cyl + hp, data = mtcars),lm(mpg ~ cyl + hp, data = mtcars))
```

